The FAIRification of research in real-world evidence: A practical introduction to reproducible analytic workflows using Git and R

### 2023-11-23 manuscript/manuscript.qmd
added details regarding code documentation, codebooks and relevance and challenges of Git in diverse RWE teams (as per R#3 comments)

To document the structure and location of files, we can include this, and other critical information about the project, in the `README.md` file. This file can be auto-generated when a project is initialized through a remote repository (see prior step in @sec-gui-initialization-and-git-clone) or can be manually added afterwards by creating a text file with the name `README.md` in the root directory of the repository. It is critically important to use the `README.md` file to provide essential instructions and information about the repository and the corresponding project. This should include a brief summary about the project's background and objectives, instructions on how to install software or manage computation environments and dependencies, details regarding codebooks, important files and the organization of the repository, contribution guidelines, contact information and the project's license to outline the terms under which others can use, modify, and distribute the project. Especially for open-source software projects choosing a suitable license is critical for which GitHub provides helpful guidance and information under <https://choosealicense.com/>.

@@

Finally, code sharing can enable researchers to learn from each other, build trust[@orsini2020], expedite the uptake of novel methodologies and knowledge exchange and decrease unnecessary redundancies through sharing of code libraries, functions and algorithms.

>>>>

All relevant metadata, instructions and information about a project should be documented in the `README.md` file. This file can be auto-generated when a project is initialized through a remote repository (see prior step in @sec-gui-initialization-and-git-clone) or can be manually added afterwards by creating a text file with the name `README.md` in the root directory of the repository. Essential information to include contain a brief summary about the project's background and objectives, instructions on how to install software or manage computation environments and dependencies, important files and the organization of the repository, contribution guidelines, contact information and the project's license to outline the terms under which others can use, modify, and distribute the project. Especially for open-source software projects choosing a suitable license is critical for which GitHub provides helpful guidance and information under <https://choosealicense.com/>.

A special aspect about real-world data, such as administrative insurance claims and electronic health records, is that these data are typically not collected for the primary purposes of doing research but rather for reasons of billing or clinical documentation. Hence, being transparent about the data provenance, pre-processing steps and operationalization of exposures, outcomes and covariates is of critical importance [@wang2017] and should be part of the repository's metadata. This can come in form of codebooks, data dictionaries or other applicable documentation files. Applying and documenting naming conventions of files, data structures and variables as developing reproducible and well documented functions or packages as well as inline commenting of programming code can further enhance the transparency and readability of analytic code.[@bové2023improving]

@@

Finally, code sharing can enable researchers to learn from each other, build trust[@orsini2020], expedite the uptake of novel methodologies and knowledge exchange and decrease unnecessary redundancies through sharing of code libraries, functions and algorithms. `Git` was primarily designed for version control and development of analytic code by statisticians and programmers, but may also benefit other members of a RWE generation team through the centralized deployment, tracking and version control of study documents as well as project management tools which have become standard among most established remote repository platforms. While `Git` offers substantial benefits for collaboration, reproducibility, and transparency in RWE teams, challenges can arise in its adoption, particularly related to merging conflicts, steep learning curves, and maintaining consistent usage practices across team members.
